A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-14 main.tex
Updates from Overleaf

%\end{MyColorPar}
%%%%%% end of additional revision1
\par
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
However, there are three challenges of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}. Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.x. \acrshort{tcga}). After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. The above mentioned web-tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.

>>>>

%\end{MyColorPar}
%%%%%% end of additional revision1
\par
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
However, there are three challenges of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}. Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.x. \acrshort{tcga}). After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. The above mentioned web-tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
